---
title: "HTML Slides"
author: "Julia Clark"
date: "March 16, 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
knitr::opts_chunk$set(echo = TRUE) # change to echo=FALSE to turn echo permanently off
# Loading required libraries
list.of.packages <- c("foreign", "stargazer", "sandwich", "haven", "ggplot2", "plotly")

# Chicking if library installed, installed if not. 
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages)) install.packages(new.packages, repos= "http://cran.cnr.berkeley.edu/") 

# Calling libraries 
lapply(list.of.packages, require, character.only = TRUE)
```

## HTML Slides in RMarkdown

You can also use R Markdown to make slides. These can be in pdf (beamer) format, or in HTML, as in this example. The principles are the same; make new slides and add content in Markdown and R.Then click "knit" and open the resulting file in any web browser. 

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plotly Histogram
Since we're doing HTML and now PDF, we can make some cool interactive graphs using `plotly`:

```{r, echo=FALSE, message=FALSE}
# 
# need <- c("plotly") # list packages you need
# have <- need %in% rownames(installed.packages()) # see which are already
# if(any(!have)) install.packages(need[!have]) # installs the missing ones 
# invisible(lapply(need, library, character.only=T)) # then loads them all

plot_ly(x = rnorm(500), type = "histogram")

```

## Percent College Graduates in US Midwestern States
```{r, echo = FALSE, message = FALSE}

plot_ly(midwest, x = ~percollege, color = ~state, type = "box")

```

## US Unemployment Rate Over Time
```{r, echo = FALSE, message = FALSE}

plot_ly(economics, x = ~date, y = ~unemploy / pop)

```

## Iris Data
```{r, echo = FALSE, message = FALSE}

plot_ly(data = iris, x = ~Sepal.Length, y = ~Petal.Length, color = ~Species)

```

## A Choropleth Map
```{r, echo = FALSE, message = FALSE}

plot_ly(type = 'choropleth', 
        locations = c('AZ', 'CA', 'VT'), 
        locationmode = 'USA-states', 
        colorscale = 'Viridis', 
        z = c(10, 20, 40)) %>% layout(geo=list(scope = 'usa'))

```

